% ----------------------------------------------------
% Conclusions
% ----------------------------------------------------


\documentclass[class=report,11pt,crop=false]{standalone}
\input{../Style/ChapterStyle.tex}
\input{../FrontMatter/Glossary.tex}
\begin{document}
\ifstandalone
\tableofcontents
\fi
\section{Conclusions \label{ch:conclusions}}

The purpose of this task was to construct an ML model for instrument classification. The report began with a short introduction, followed by a literature review. Here, information was gathered on how to properly go about this task. The data was then collected from various sites, and different methods of feature extraction were performed to extract the relevant input features. The ML model creation was then explained. With enough information, the core objectives were then outlined, and investigated in testing. 

In testing, the deeper neural network tended to overfit the data more frequently, which is why a shallower neural network was preferred, despite yielding a lower model accuracy. With regards to the various windowing methods, the model trained with data processed with a rectangular window proved to be the best, which implied that the neural network was more sensitive to frequency resolution over spectral leakage. MFCCs were briefly examined, including being trained on a custom CNN using a horizontal kernel. Though the horizontal kernel did appear to yield better results, the overall performance of the MFCCs was comparable to that of the spectrograms.

Given these conclusions, the model was retrained on all the training data, and evaluated on the test data to gain a concrete idea of the model's real-world performance. The final model accuracy was quoted at 74.2\%. Given that the model was trained on unfiltered data, this is rather impressive.

% ----------------------------------------------------
\ifstandalone
\bibliography{../Bibliography/References.bib}
\printnoidxglossary[type=\acronymtype,nonumberlist]
\fi
\end{document}
% ----------------------------------------------------